---
title: "Data Cleaning: Exercises"
format: 
  html:
    code-fold: true
    code-summary: "Show the code solution"
---

# Instructions:

**Recommended:** Complete these exercises in the dedicated R in Pharma RStudio Cloud work space, which comes with 

1. all packages pre-installed, and

2. an Rmarkdown document to fill in.

It may still be helpful to peek here to verify that your tables match the 
desired output.

[Click here to enter R/Medicine Posit cloud work space](https://rstudio.cloud/spaces/299322/join?access_code=Vnp96stsVIDLiEJI7AtHAQ4GB1gsptQgnOGb99_N){target="_blank"}

**Otherwise:** Follow along this document, work on your personal computer, 
and challenge yourself not to peek at the code solutions until you have completed
the exercise.

# Packages

```{r}
#| label: packages
#| message: false
#| echo: true
#| code-fold: false
#| warning: false
library(tidyverse)
```


# The Data

data details

# Exercise 1

view first six rows of `mtcars`

```{r}
head(mtcars)
```

# Exercise 2


# Session info

```{r}
#| label: session-info
#| eval: true
#| code-fold: false
devtools::session_info()
```

