---
title: "Pre-work"
format: html
---

## Participation

Demonstrations and exercises will be in [Posit Cloud](https://posit.cloud/).
Posit Cloud allows us all to work in the exact same environment with the same
version of R, R packages, and directory of files. Please create an account if
you don't yet have one.

You must be part of the CEDS Workshops Posit Cloud work space to access the
project linked below.

[**https://posit.cloud/spaces/504211/content/8093007**](https://posit.cloud/spaces/504211/content/8093007){.uri}

**Alternative**

If you are struggling with Posit Cloud or if you prefer to work locally, please
have the following installed and configured on your machine.

-   Recent version of [**R**](https://cran.rstudio.com/),
    [**RStudio**](https://posit.co/download/rstudio-desktop/), and
    [**Quarto**](https://quarto.org/docs/get-started/)

-   Recent version of packages used in this workshop:

    ```{r}
    #| eval: false

    pkgs <- c("dplyr", "fs", "ggplot2", "here", "plotly", "purrr", "quarto", 
              "readr", "stringr", "janitor", "lubridate", "tidyr", "rmarkdown",
              "knitr")

    install.packages(pkgs)
    ```

-   Check that Quarto works on your computer:

    1.  Open RStudio and create a new Quarto (`.qmd`) document.

    2.  Save the document and check you are able to render it.

-   Get the project on your machine (by default, downloads to desktop).
    
    Uncomment and use the `destdir` argument to choose a different location.

    ```{r}
    #| eval: false

    # install.packages("usethis")
    usethis::use_course(
        "https://github.com/jadeynryan/parameterized-quarto-workshop/raw/coa-ceds/exercises/ceds-quarto-exercises.zip"
        # , destdir = "C:/Users/jryan/Documents/R/projects"
    )
    ```

## Quarto and `purrr` {#sec-quarto-purrr}

If you're new to Quarto, we recommend watching [Mine Çetinkaya-Rundel's
23-minute *Getting Started with
Quarto*](https://www.youtube.com/watch?v=_f3latmOhew) or [Tom Mock's 2-hour
*Welcome to Quarto Workshop*](https://www.youtube.com/watch?v=yvi5uXQMvu4).

If you're new to `purrr`, we recommend watching this R-Ladies Baltimore
presentation [*Make your R Code purr with
`purrr`*](https://www.youtube.com/watch?v=IewsPpjKElc) and reviewing Jenny
Bryan's [tutorial](https://jennybc.github.io/purrr-tutorial/) and
[workshop](https://github.com/jennybc/row-oriented-workflows).
