---
title: "Pre-work"
---

This workshop will largely be conducted in the Posit Cloud environment. Please create a login to the Posit Cloud instance of this workshop here:

**[bit.ly/rladies-parameterized-quarto](https://bit.ly/rladies-parameterized-quarto)**.

If you will not be using the Posit Cloud instance, you can learn by watching and listening.

As a more high-risk alternative, if you would like to try this out on your own computer, please have the following installed and configured on your machine. Note that we will **NOT** be able to help you with local computer problems during the workshop. If you choose to do this, you are on your own.

-   Recent version of **R**

-   Recent version of **RStudio**

-   Recent version of packages used in this workshop:

    ``` {r}
    #| eval: false

    pkgs <- c("dplyr", "fs", "ggplot2", "here", "plotly", "purrr", "quarto", 
              "readr", "stringr", "janitor", "lubridate", "tidyr", "rmarkdown",
              "knitr")

    install.packages(pkgs)
    ```

-   Check that Quarto works on your computer:

    1. Open RStudio and create a new Quarto (`.qmd`) document.

    2. Save the document and check you are able to render it.

-   Get the project on your machine.

    ```{r}
    #| eval: false

    # install.packages("usethis")
    usethis::use_course("https://github.com/jadeynryan/rladies-parameterized-quarto/raw/main/exercises/exercises.zip")
    ```
