---
title: "Pre-work"
---

This workshop has five exercises for you to try. After the workshop, I encourage you to adapt the exercise template files and code to fit your own projects.

There are three ways for you to participate. Please complete the pre-work for whichever way you'd like to follow along **before the workshop**. Spinning up the Posit Cloud instance can take a few minutes, as can installing packages and downloading the exercises.

## Follow along in the Posit Cloud

This workshop will largely be conducted in the [Posit Cloud](https://posit.cloud/) environment. Posit Cloud allows us all to work in the exact same environment with the same version of R, R packages, and directory of files. Please create an account if you don't yet have one.

**Join the R-Ladies workspace**: [bit.ly/rladies-parameterized-quarto](https://bit.ly/rladies-parameterized-quarto).

**Open the R-Ladies Abuja project**:
[bit.ly/quarto-params-posit-cloud](https://bit.ly/quarto-params-posit-cloud).

## Watch and listen

If you will not be using the Posit Cloud instance, you can learn by watching and listening. No pre-work needed for you. 😊

## Follow along on your own computer

As a more high-risk alternative, if you would like to try this out on your own computer, please have the following installed and configured on your machine. Note that we will **NOT** be able to help you with local computer problems during the workshop. If you choose to do this, you are on your own.

-   Recent version of **R**

-   Recent version of **RStudio**

-   Recent version of packages used in this workshop:

    ``` {r}
    #| eval: false

    pkgs <- c("dplyr", "fs", "ggplot2", "here", "plotly", "purrr", "quarto", 
              "readr", "stringr", "janitor", "lubridate", "tidyr", "rmarkdown",
              "knitr")

    install.packages(pkgs)
    ```

-   Check that Quarto works on your computer:

    1. Open RStudio and create a new Quarto (`.qmd`) document.

    2. Save the document and check you are able to render it.

-   Get the project on your machine. Fill in `destdir` with the location where you want to download the project. Delete that argument if you want it to default to your Desktop.

    ```{r}
    #| eval: false

    # install.packages("usethis")
    usethis::use_course(
        "https://github.com/jadeynryan/parameterized-quarto-workshop/raw/main/exercises/exercises.zip",
        destdir = "___")
    ```

## Quarto and {purrr} {#sec-quarto-purrr}

If you're new to Quarto, we recommend watching [Tom Mock's excellent 2-hour introduction to Quarto](https://www.youtube.com/watch?v=yvi5uXQMvu4).

If you're new to {purrr}, we recommend watching this R-Ladies Baltimore presentation [*Make your R Code purr with purrr*](https://www.youtube.com/watch?v=IewsPpjKElc) and reviewing Jenny Bryan's [tutorial](https://jennybc.github.io/purrr-tutorial/) and [workshop](https://github.com/jennybc/row-oriented-workflows).
