---
title: "Pre-workshop instructions"
format: html
execute: 
  eval: false
---

Prior to the workshop, please complete the following steps:

*If you have trouble with these steps, or you'd prefer not to mess with your current set up, you can also work in Posit Cloud. See [Backup option](#backup-option-posit-cloud) below.*


#### 1. Software

Download and install the latest versions of R, RStudio, and Quarto:

-   R 4.2.3 or above: <https://cran.r-project.org>
-   RStudio 2024.04.0 or above: <https://posit.co/download/rstudio-desktop>
-   Quarto 1.4 or above: <https://quarto.org/docs/download> 

#### 2. R Packages

Install the following packages by copying and pasting the following into the console in RStudio:

```{r}
install.packages(c("dplyr", "fs", "ggplot2", "here", "janitor", "knitr", 
                    "lubridate", "plotly", "purrr", "quarto", "readr", 
                    "rmarkdown", "stringr", "tidyr"))
```

#### 3. Exercises

Download and open the exercises for this workshop by copying and pasting the following into the console in RStudio:

This will download the RStudio project onto your Desktop. To choose a different destination, uncomment and use the `destdir` argument.

```{r}
# install.packages("usethis")
usethis::use_course(
  "https://github.com/jadeynryan/parameterized-quarto-workshop/raw/cascadia/exercises/intermediate-exercises.zip"
# , destdir = "C:/Users/jryan/Documents/R/projects"
  )
```

If `use_course()` didn't work, manually download the zip file from GitHub: [github.com/jadeynryan/parameterized-quarto-workshop/tree/cascadia/exercises](https://github.com/jadeynryan/parameterized-quarto-workshop/tree/cascadia/exercises).

## Backup option: Posit Cloud

You can choose to use Posit Cloud instead which has the required tools already installed, along with a copy of the exercise files. Join the Posit Cloud [Quarto Cascadia workspace](https://posit.cloud/spaces/519059/join?access_code=ckv18LHEcSw3QtQ904uvpzLVlh4L2rk6RhKdpwyp) and open the [Intermediate Exercises project](https://posit.cloud/spaces/519059/content/8351107).

## `purrr` {#sec-purrr}

If you're new to `purrr`, we recommend watching this R-Ladies Baltimore
presentation [*Make your R Code purr with
`purrr`*](https://www.youtube.com/watch?v=IewsPpjKElc) and reviewing Jenny
Bryan's [tutorial](https://jennybc.github.io/purrr-tutorial/) and
[workshop](https://github.com/jennybc/row-oriented-workflows).
