---
execute:
  eval: false
---

# Conditional content {.section}

## Control content visibility

Special `.content-visible` and `.content-hidden` classes can be applied to:

**Divs**

``` markdown
::: {.content-visible when-format="html"}

Will only appear in HTML.

:::
```
. . .

**Non-executable code**

```{.python .content-visible when-format="html"}
# code shown only in HTML
2 + 2
```

. . .

**Spans**

``` markdown
Some text
[in HTML.]{.content-visible when-format="html"}
[in PDF.]{.content-visible when-format="pdf"}
```

::: footer
Examples from [Conditional Content Quarto docs](https://quarto.org/docs/authoring/conditional.html)
:::

## Useful for static/interactive features

Pairs well with `{{< include >}}` shortcodes to re-use content without copying/pasting.

Use an underscore `_` prefix for included files so they are automatically ignored by a Quarto render of a project ([Includes Quarto Docs](https://quarto.org/docs/authoring/includes.html)).

::::: panel-tabset

## Static

Use `.content-visible unless-format="html"`

```markdown
:::: {.content-visible unless-format="html"}

## Cats

{{{< include _cats.qmd >}}}

## Dogs

{{{< include _dogs.qmd >}}}

::::
```

## Interactive

Use `.content-visible when-format="html"`

```markdown
:::: {.content-visible when-format="html"}
::: panel-tabset

## Cats

{{{< include _cats.qmd >}}}

## Dogs

{{{< include _dogs.qmd >}}}

:::
::::
```
:::::

# 💪🏼 Exercise 4 {.exercise}

1. Modify `ex-4-conditional-content.qmd` so that the `panel-tabset` is only used for HTML documents by filling in the `{.content-`} class.

Options:

 - {.content-visible when-format="___"}
 
 - {.content-visible unless-format="___"}
 
 - {.content-hidden unless-format="___"}
 
 - {.content-hidden unless-format="___"}
 
 2. 💬 **Chat**: what other kinds of content might you want to make visible for only a certain format?

```{r}
#| echo: false
countdown::countdown(minutes = 5, top = 0)
```

## Conditional code execution

::: incremental

-   More efficient to not execute code that generates interactive outputs for static reports.

-   Useful for executing interactive plot code for HTML reports and static `ggplot2` code for all other formats. 

-   Not currently a feature of Quarto v1.3, but a Quarto dev thinks it could be possible in v1.4 according to this [GitHub discussion](https://github.com/quarto-dev/quarto-cli/discussions/3260#discussioncomment-4573926). Granted, that comment was from 2023-01-02...

:::

## Workaround for conditional R code

Include in the setup chunk of your `.qmd` file.

Get the format of the Pandoc output:

```{r}
#| label: setup
#| echo: fenced

# Get output format
format <- knitr::opts_knit$get("rmarkdown.pandoc.to")
```

## Use `eval: !expr` chunk option

::: panel-tabset

## Static plot

```{r}
#| echo: fenced
#| eval: !expr format %in% c("latex", "docx")

# code to create static {ggplot2}
```

## Interactive plot

```{r}
#| echo: fenced
#| eval: !expr format == "html"

# code to create interactive {plotly}
```

:::

<br>

. . .

**Can even use `params` in `!expr`:**

``` r
#| eval: !expr params$fave_breed == "Snowshoe"
```

. . .

<br>

[Chunk Options Quarto Docs](https://quarto.org/docs/computations/r.html#chunk-options)

# 💪🏼 Exercise 5 {.exercise}

1. Modify `ex-5-conditional-code.qmd` so that code chunks for `ggplot2` are executed only for PDF or MS Word documents and code chunks for `plotly` are executed only for HTML documents.

    Hints:
   ```r
   # Get output format in setup chunk:
   format <- knitr::opts_knit$get("rmarkdown.pandoc.to")

   # Set chunk option:
   #| eval: !expr format == "html"
   ```

2. 💬 **Chat**: what is something you learned from this workshop that you're excited to apply to your own reports and projects?

```{r}
#| echo: false
countdown::countdown(minutes = 5, top = 0)
```
