---
execute:
  eval: false
---

<!-- # Conditional content {.section} -->

<!-- ## Control content visibility -->

<!-- Special `.content-visible` and `.content-hidden` classes with `when-format="___"` and `unless-format="___"` attributes can be applied to: -->

<!-- ::: panel-tabset -->

<!-- ## Divs -->

<!-- ```markdown -->
<!-- ::: {.content-visible when-format="html"} -->

<!-- Will only appear in HTML. -->

<!-- ::: -->
<!-- ``` -->

<!-- ## Spans -->

<!-- ``` markdown -->
<!-- Some text -->
<!-- [in HTML.]{.content-visible when-format="html"} -->
<!-- [in PDF.]{.content-visible when-format="pdf"} -->
<!-- ``` -->

<!-- ## Non-executable code -->

<!-- Fenced code blocks purely for documentation. -->

<!-- ````markdown -->
<!-- ```{.python .content-visible when-format="html"} -->
<!-- # code shown only in HTML -->
<!-- 2 + 2 -->
<!-- ``` -->
<!-- ```` -->

<!-- ::: -->

<!-- ::: footer -->
<!-- Examples from [Conditional Content Quarto docs](https://quarto.org/docs/authoring/conditional.html) -->
<!-- ::: -->

<!-- ## Useful for static/interactive features -->

<!-- Pairs well with `{{< include >}}` shortcodes to re-use content without copying/pasting. -->

<!-- . . . -->

<!-- ::::: panel-tabset -->

<!-- ## Static -->

<!-- ```markdown -->
<!-- :::: {.content-visible unless-format="html"} -->

<!-- ## Cats -->

<!-- {{{< include _cats.qmd >}}} -->

<!-- ## Dogs -->

<!-- {{{< include _dogs.qmd >}}} -->

<!-- :::: -->
<!-- ``` -->

<!-- ## Interactive -->

<!-- ```markdown -->
<!-- :::: {.content-visible when-format="html"} -->
<!-- ::: panel-tabset -->

<!-- ## Cats -->

<!-- {{{< include _cats.qmd >}}} -->

<!-- ## Dogs -->

<!-- {{{< include _dogs.qmd >}}} -->

<!-- ::: -->
<!-- :::: -->
<!-- ``` -->
<!-- ::::: -->

<!-- . . . -->

<!-- Use an underscore prefix for included files so they are automatically ignored by a Quarto render of a project ([Includes Quarto Docs](https://quarto.org/docs/authoring/includes.html)). -->

<!-- # ðŸ’ªðŸ¼ Exercise 4 {.exercise} -->

<!-- **Use conditional content divs to control when tabsets are shown.** -->

<!-- 1. Modify `ex-4-conditional-content.qmd` so that the `panel-tabset` is visible for HTML reports and hidden for all other formats. -->

<!-- <br> -->

<!-- 2. Explore the other options. There are multiple ways to get the same result. -->

<!--     {.content-visible when-format="html"} == {.content-hidden unless-format="html"} -->

<!-- <br> -->

<!-- 3. ðŸ’¬ **Chat**: what other kinds of content might you want to make visible for only a certain format? -->

<!-- ```{r} -->
<!-- #| echo: false -->
<!-- countdown::countdown(minutes = 5, top = 0) -->
<!-- ``` -->

# Conditional code execution {.section}

## Conditionally execute a code chunk

::: incremental

-   More efficient to not execute code that generates interactive outputs for static reports.

-   Useful for executing interactive plot code (e.g., `plotly` or `ggiraph`) for HTML reports and static `ggplot2` code for all other formats. 

-   Useful for executing different code based on a parameter value.

-   Not currently a feature of Quarto v1.4. Follow along with this [GitHub discussion](https://github.com/quarto-dev/quarto-cli/discussions/3260#discussioncomment-4573926).

-   Chunk options can use R code for option values with `!expr`. Learn about the limitations to this YAML "tag" literal syntax in the [Quarto Chunk Options reference](https://quarto.org/docs/computations/r.html#chunk-options).

:::

## Conditional code based on output

Include in the setup chunk of your `.qmd` file.

Get the format of the Pandoc output:

```{r}
#| label: setup
#| echo: fenced

# Get output format
format <- knitr::opts_knit$get("rmarkdown.pandoc.to")
```

## Use `eval: !expr` chunk option

::: panel-tabset

## Static plot

```markdown
#| echo: fenced
#| eval: !expr format %in% c("latex", "docx")

# code to create static {ggplot2}
```

ðŸ’¡ Pandoc uses LaTeX to create PDFs.

## Interactive plot

```markdown
#| echo: fenced
#| eval: !expr format == "html"

# code to create interactive {plotly}
```

:::

# ðŸ’ªðŸ¼ Exercise 5 {.exercise}

<br>

**Conditionally execute `ggplot2` code for static reports & `plotly` code for interactive reports.**

1. Open `ex-5-conditional-code.qmd`.

2. Fill in the blanks for the `eval: ` option for `ggplot` code chunks and `plotly` code chunks.

3. ðŸ’¬ **Discuss**: How would you change the `eval: ` option to execute a chunk based on a parameter value rather than the output format?

```{r}
# Options are html, latex, and docx.

#| eval: !expr format == "___"

#| eval: !expr format %in% c("___", "___")
```

```{r}
#| echo: false
countdown::countdown(minutes = 5, top = 0)
```

## Conditional code based on parameter

Use `params` in `!expr`:

``` r
#| eval: !expr params$fave_breed == "Snowshoe"

# Code for a special plot for my favorite cat breed.
```

<br>

. . .

``` r
#| eval: !expr !params$fave_breed == "Snowshoe"

# Code for a different plot for all other breeds.
# Note the ! in front of params.
```

<br>

. . .

::: callout-tip
## Community project: home energy monitoring
Consider using a different conditional code chunk to create different visualizations depending on heating source.
:::
